---
title: "Basic Image Classification with TensorFlow"
subtitle: "R Sample Code"
output: pdf_document
geometry: margin=2cm
fontsize: 12pt
---

## Libraries

Load TensorFlow and Keras libraries.
\
```{r}
library(tensorflow)
library(keras)
```

## Dataset

Load the MNIST dataset and scale the pixel values to the range of [0,1].
\
```{r}
c(c(x_train, y_train), c(x_test, y_test)) %<-% keras::dataset_mnist()
x_train <- x_train / 255
x_test <-  x_test / 255
```

## Artificial Neural Network Model

Define a fully-connected feedforward artificial neural network architecture with a single hidden layer composed of 128 neurons. Set the dropout rate at 20%.
\
```{r}
model <- keras_model_sequential(input_shape = c(28, 28)) %>%
  layer_flatten() %>%
  layer_dense(128, activation = "relu") %>%
  layer_dropout(0.2) %>%
  layer_dense(10)
```
\
Define the loss function, the optimizer, and the evaluation metric for the training.
\
```{r}
loss_fn <- loss_sparse_categorical_crossentropy(from_logits = TRUE)
```
\
```{r}
model %>% compile(
  optimizer = "adam",
  loss = loss_fn,
  metrics = "accuracy"
)
```

## Model Training and Evaluation

Fit the model on the training set.
\
```{r}
model %>% fit(x_train, y_train, epochs = 5)
```
\
Evaluate the classification performance of the model on the test set.
\
```{r}
model %>% evaluate(x_test,  y_test, verbose = 2)
```








